Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-02-21 article.rnw
Flag as an incomplete sentence as a TODO.

In the statistical literature, regularisation is the process of using external information to prevent overfitting or to solve an otherwise overspecified problem \parencite{XXX}. One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{XXX}. XXX why this could be a problem XXX
Alternatively, one can assume that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species,weiss2021disentangling}.

>>>>

In the statistical literature, regularisation is the process of using external information to prevent overfitting or to solve an otherwise overspecified problem \parencite{XXX}. One simplifying approach is to assume that most pairs of species do not interact or interact weakly, and hence setting many of the parameters to zero \parencite{XXX}. %TODO: XXX why this could be a problem XXX.
Alternatively, one can assume that species fall into groups, such that all species in the same group interact with species in other groups in an identical fashion, thereby collapsing pairwise interaction parameters for all the species in that group into sets of common parameters \parencite{ovaskainen2017species,weiss2021disentangling}.
